%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Recent Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Solution Principal} % Job title
    {Slalom LLC} % Organization
    {Atlanta, GA} % Location
    {Sep. 2018 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Plan and execute technology projects for clients.}
        \item {Lead technology decisions, day to day activities at client location inline with the client’s long-term goals.}
        \item {Assist in writing SOWs and proposals for future work.}
        \item {Currently managing 3 engineers, mentoring the engineers with a view to improve their skills and guide them to be leaders in the future.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
  {Director Professional Services} % Job title
  {Jacada Inc} % Organization
  {Atlanta, GA} % Location
  {Nov. 2013 - Sep. 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Oversight over multiple client projects.}
      \item {Technology oversight for the whole practice, driving knowledge sharing and best practices.}
      \item {Manage time and material delivered to the client to maintain a mutually successful relationship.}
      \item {Step in and help resolve any conflicts or escalations.}
      \item {Act as a safety check with any technology decisions to ensure long term client goals are considered.}
      \item {Responsible for hire and performance of 5-15 employees depending on workload.}
      \item {Take technology lead in building POCs for sales initiatives. Help shape solutions to client needs.}
    \end{cvitems}
  }
%---------------------------------------------------------

\end{cventries}
