%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Recent Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
{Slalom LLC} % Organization
{NCR} % Employer
{Atlanta, GA} % Location
{Sep. 2019 - Current} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Leading the migration of their SMB product called Silver from AWS to GCP.}
    \item {Helped sell additional scope after an initial small assignment to help with specific technology problems the customer was looking to solve.}
    \item {Automated install of complex custom configurations, for e.g. a highly customized SQL Server implementation on custom compute instances.}
    \item {Built solution to cutover with minimal downtime taking into consideration security requirements of NCR affecting this timeline.}
    \item {Architected a solution for failover across AWS and GCP cloud.}
    \item {Leading efforts to instill a DevOps culture.}
    \item {Coordinated work between Google, Slalom and NCR to find solutions for GCP specific quirks.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Slalom LLC} % Organization
{The Home Depot} % Employer
{Atlanta, GA} % Location
{Sep. 2018 - Oct. 2019} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Delivered a solution to facilitate retirement of their \$2B payments system.}
    \item {Executed the plan ahead of schedule, allowing the customer to plan future tasks.}
    \item {Helped the customer unentangle their internal dependency spaghetti allowing them to streamline the future work based on current team workload.}
    \item {Came up with a strategy to allow the customer to safely sunset their, monolithic, hard to maintain system, which was expensive and hard to scale.}
    \item {Led a major undertaking to shine a light on the system, with in depth analysis of code.}
    \item {Our documentation captured all the stop gaps solutions in place for several years for core business components like their web store payment and paid for years of technical debt.}
    \item {Assimilated all the tribal knowledge which was key to the maintenance and history of the system.}
    \item {Due to the lack of comprehensive test plan, tailor made a migration plan to allow parallel execution without affecting downstream systems.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Jacada Inc} % Organization
{Microsoft} % Employer
{Atlanta, GA} % Location
{Nov. 2015 - Aug. 2018} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Designed and implemented a public facing solution to be an alternative for their IVR.}
    \item {Built an exceptional relationship with the client helping the client become successful internally. Our client was promoted as a result of the project's success.}
    \item {Sold multiple renewals for support and new work, with the project becoming one of Jacada’s biggest success stories.}
    \item {Redirected our learnings on the project using the early release of Jacada's SaaS product allowed the product team to make the product more robust and marketable to other customers.}
    \item {Developed several custom JavaScript plugins to customize the solution.}
    \item {Built and maintained a custom backend API in Azure cloud to ease integration pains with Microsoft infrastructure, as a side effect we were one of the first 3rd parties to use Azure AD and many other Azure cloud products.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Jacada Inc} % Organization
{American National} % Employer
{Atlanta, GA} % Location
{Sep. 2017 - Aug. 2018} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Designed their call center application.}
    \item {Leadership oversight on the project while managing the scope.}
    \item {Oversaw their deployment to production, being the feet on the ground as the customer deployed to their workforce.}
    \item {Developed a custom JavaScript framework to minimize rework and allow for reuse and extensibility.}
    \item {Assisted their infrastructure admins to deploy the solution across various lifecycles.}
  \end{cvitems}
}

%---------------------------------------------------------
\cventry
{Jacada Inc} % Organization
{Humana} % Employer
{Atlanta, GA} % Location
{May. 2016 - Jan. 2017} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Implemented a Micro-Services architecture.}
    \item {Championed an API first approach.}
    \item {Designed a timer-based solution to enable asynchronous submission of user data to backend system.}
    \item {Led UI/UX design while keeping in line with business feedback.}
    \item {Orchestrated of development tasks while working with a geographically spread teams across the world.}
    \item {Created a framework with an eye on future enhancements that other developers could follow.}
    \item {This framework helped save 20\% development time planned for the rest of the project along with a non trivial drop in bug occurrence.}
  \end{cvitems}
}
%---------------------------------------------------------

\end{cventries}
